The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2024-09-30 example.tex
Adjustments for modern stats basic block layout. Fixed quotation/aside font selection in default font set.
Some updates to the example document; notes on aside & quotation environments, examples & info on modern stat blocks.

\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode,stats=modern]{dndbook}

@@

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}

@@

@@

@@

The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block

>>>>

\documentclass[letterpaper,twocolumn,openany,nodeprecatedcode]{dndbook}

@@

\usepackage[utf8]{inputenc}
\usepackage[singlelinecheck=false]{caption}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{shortvrb}
\usepackage{stfloats}
\usepackage{wrapfig}

@@

The |DndQuotation| environment goes a little further, offering the option of comment attribution, and tilts the note at a slight angle.

@@

    % If you want to use commas in the key values, enclose the values in braces.
    \DndMonsterBasics[
        armor-class = {9 (12 with \emph{mage armor})},
        hit-points  = {\DndDice{3d8 + 3}},
        speed       = {30 ft., fly 30 ft.},
      ]

    \DndMonsterAction{Innate Spellcasting}
    Foo's spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It can innately cast the following spells, requiring no material components:
    \begin{DndMonsterSpells}
      \DndInnateSpellLevel{misty step}
      \DndInnateSpellLevel[3]{fog cloud, rope trick}
      \DndInnateSpellLevel[1]{identify}
    \end{DndMonsterSpells}

The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.

When used with the |stats=modern| package option, some additional values are available for customization: |DndMonsterBasics| takes an |initiative| option to display as part of the initial block; it appears to the right of the \textbf{Armor Class} option. The |DndMonsterAbilityScores| command now has options for |str save|, |dex save|, etc, which if provided will replace the values in the appropriate \textbf{save} column of the abilities block. Lastly, modern stat blocks use an explicit section title for traits (the actions appearing between |DndMonsterDetails| and the \textbf{Actions} section). WotC also seems to have moved most \textbf{Spellcasting} blocks into the \textbf{Actions} section, though whether you also do this is a matter of personal style.

%% Manually toggle a bunch of internals to produce a modern stat block as an example.
%% This will happen automatically if you use the |stats=modern| package option.

\ExplSyntaxOn
\let\DndMonster\DndMonsterModernBg
\let\endDndMonster\endDndMonsterModernBg
\bool_set_true:N \l__dnd_modern_stats_bool
\ExplSyntaxOff

@@

\ExplSyntaxOn
\bool_set_false:N \l__dnd_modern_stats_bool
\let\DndMonster\DndMonsterClassicBg
\let\endDndMonster\endDndMonsterClassicBg
\ExplSyntaxOff
